*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-22 Code/Manuscript_O2.Rmd
edits to subheadings

### MED4 Clade HLI  {.unnumbered}
The GAM model in Figure \@ref(fig:MED4GAM) shows MED4 growth in response to red (A) or blue (B) peak PAR and photoperiod across 2 imposed oxygen concentrations.  Under 250 µM O~2~ MED4 achieved fastest growth rates above peak blue light of ~180 µmol photons m^-2^ s^-1^, and the longest photoperiod of 16, indicated by the 0.69 d^-1^ contour line representing the
90^th^ percentile of maximum achieved growth rate.  Growth decreased with decreasing photoperiod and peak PAR.  Under red light growth was generally slower but the pattern of growth responses to photoperiod and PAR was similar.  We again note the exclusion of MED4 from growth under 4 h photoperiod. Under 25 µM O~2~ MED4 showed similar growth responses, but was excluded from both 4 and 8 h photoperiods.

@@

The GAM model in Figure \@ref(fig:SS120GAM) shows growth
responses of SS120 red (A) or blue (B) peak PAR and photoperiod,
across the 2 imposed oxygen concentrations. Under 250 µM O~2~,
Figure \@ref(fig:SS120GAM)A showed highest growth
rates achieved below PAR of 50 µmol photons m^-2^ s^-1^ and
photoperiods between 8 and 12 h, indicated by the contour line labeled
0.29 d^-1^ (representing the 90^th^ percentile of achieved growth rate). Note the disjunct regions of the plots, resulting from variable growth successes of SS120 under 250 µM O~2~.  Growth rate patterns under red light were similar, although somewhat faster.
In contrast, under 25 µM O~2~ and a photoperiod of 8 h SS120 exploited all blue peak PAR levels, achieving faster growth rates at a higher PAR of \~100 µmol photons
m^-2^ s^-1^, indicated by the contour line labeled 0.5 d^-1^
(representing the 90^th^ percentile of achieved growth rate), out pacing
the 90^th^ percentile fastest growth rates under 250 µM O~2~. Under red light and 25 µM O~2~ light SS120 grew across most conditions of peak PAR and photoperiod, achieving fastest growth under long photoperiods and peak PAR below 50 \~100 µmol photons
m^-2^ s^-1^.  Thus, the designation of SS120 as a LL strain is dependent upon the [O~2]. SS120 did not, however,  grow under tested conditions at 2.5 µM O~2~.

@@

The GAM model in Figure \@ref(fig:MIT9313GAM) shows MIT9313 growth responses to red (A) or blue (B) peak PAR and photoperiod. Under 250 µM O~2~,  Figure \@ref(fig:MIT9313GAM)A shows MIT9313 achieves
fastest growth rates between blue peak PAR of 30 µmol photons m^-2^
s^-1^ and 50 µmol photons m^-2^ s^-1^ and photoperiods longer than 8 h,
indicated by the contour line labeled 0.51 d^-1^ representing the
90^th^ percentile of achieved growth rates. Figure
\@ref(fig:MIT9313GAM)A also shows that growth rate increases
with longer photoperiods, as long as the blue peak PAR levels remain below 50 µmol
photons m^-2^ s^-1^.  In contrast, under red light and 250 µM O~2~ MIT9313 grows faster while exploiting higher peak PAR and longer photoperiods.  Thus the designation of MIT9313 as a LL clade is dependent upon [O2].
(Figure \@ref(fig:MIT9313GAM)B).  Figure \@ref(fig:MIT9313GAM)C
shows that MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR between 50 to 10 µmol photons
m^-2^ s^-1^ PAR (Figure \@ref(fig:MIT9313GAM)C).

@@

>>>>

The GAM model in Figure \@ref(fig:MED4GAM) summarizes MED4 growth in response to red (A) or blue (B) peak PAR and photoperiod across 2 imposed oxygen concentrations.  Under 250 µM O~2~ MED4 achieved fastest growth rates above peak blue light of ~180 µmol photons m^-2^ s^-1^, and the longest photoperiod of 16, indicated by the 0.69 d^-1^ contour line representing the
90^th^ percentile of maximum achieved growth rate.  Growth decreased with decreasing photoperiod and peak PAR.  Under red light growth was generally slower but the pattern of growth responses to photoperiod and PAR was similar.  We again note the exclusion of MED4 from growth under 4 h photoperiod. Under 25 µM O~2~ MED4 showed similar growth responses, but was excluded from both 4 and 8 h photoperiods.

@@

The GAM model in Figure \@ref(fig:SS120GAM) summarizes growth
responses of SS120 red (A) or blue (B) peak PAR and photoperiod,
across the 2 imposed oxygen concentrations. Under 250 µM O~2~,
Figure \@ref(fig:SS120GAM)A showed highest growth
rates achieved below PAR of 50 µmol photons m^-2^ s^-1^ and
photoperiods between 8 and 12 h, indicated by the contour line labeled
0.29 d^-1^ (representing the 90^th^ percentile of achieved growth rate). Note the disjunct regions of the plots, resulting from variable growth successes of SS120 under 250 µM O~2~.  Growth rate patterns under red light were similar, although somewhat faster.
In contrast, under 25 µM O~2~ and a photoperiod of 8 h SS120 exploited all blue peak PAR levels, achieving faster growth rates at a higher PAR of \~100 µmol photons
m^-2^ s^-1^, indicated by the contour line labeled 0.5 d^-1^
(representing the 90^th^ percentile of achieved growth rate), out pacing
the 90^th^ percentile fastest growth rates under 250 µM O~2~. Under red light and 25 µM O~2~ light SS120 grew across most conditions of peak PAR and photoperiod, achieving fastest growth under long photoperiods and peak PAR below 50 \~100 µmol photons
m^-2^ s^-1^.  Thus, the designation of SS120 as a LL strain is dependent upon the [O~2]. SS120 did not, however,  grow under tested conditions at 2.5 µM O~2~.

@@

The GAM model in Figure \@ref(fig:MIT9313GAM) summarizes MIT9313 growth responses to red (A) or blue (B) peak PAR and photoperiod. Under 250 µM O~2~,  Figure \@ref(fig:MIT9313GAM)A shows MIT9313 achieves
fastest growth rates between blue peak PAR of 30 µmol photons m^-2^
s^-1^ and 50 µmol photons m^-2^ s^-1^ and photoperiods longer than 8 h,
indicated by the contour line labeled 0.51 d^-1^ representing the
90^th^ percentile of achieved growth rates. Figure
\@ref(fig:MIT9313GAM)A also shows that growth rate increases
with longer photoperiods, as long as the blue peak PAR levels remain below 50 µmol
photons m^-2^ s^-1^.  In contrast, under red light and 250 µM O~2~ MIT9313 grows faster while exploiting higher peak PAR and longer photoperiods.  Thus the designation of MIT9313 as a LL clade is dependent upon [O2].
(Figure \@ref(fig:MIT9313GAM)B).  Figure \@ref(fig:MIT9313GAM)C
shows that MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR between 50 to 10 µmol photons
m^-2^ s^-1^ PAR (Figure \@ref(fig:MIT9313GAM)C).

@@

## **Prochlorococcus* genomic capacities for electron dissipation and DNA repair
NAAMAN FIGURE
Zotero BERG citation
